### 2009-04-06 talk/icooolps2009-dotnet/conclusion.tex
turn arigo into a footnote

IronPython and Jython are two popular implementations of Python for,
respectively, the CLI and the JVM, whose approach differs fundamentally from
PyPy.  The source code of PyPy contains a Python interpreter, which the JIT
compiler is automatically generated from: the resulting executable contains
both the interpreter and the compiler, so that it is possible to compile only
the desired parts of the program.  On the other hand, both IronPython and
Jython implements only the compiler: both compile code lazily (when a Python
module is loaded), but since they do not exploit the extra information
potentially available at runtime, it is more a delayed static compilation than
a true JIT one.  As a result, they run Python programs much slower than their
equivalent written in
C\#\footnote{http://shootout.alioth.debian.org/gp4/\\benchmark.php?test=all\&lang=iron\&lang2=csharp}
or
Java\footnote{http://blog.dhananjaynene.com/2008/07/performance-comparison-c-java-python-ruby-jython-jruby-groovy/}.

The \emph{Dynamic Language Runtime}\footnote{http://www.codeplex.com/dlr}
(DLR) is a library designed to ease the implementation of dynamic languages
for .NET: IronPython is based on the DLR, so the same remarks apply.

@@

In particular, the \emph{Da Vinci Machine
  Project} \footnote{http://openjdk.java.net/projects/mlvm/} is exploring and
implementing new features to ease the implementation of dynamic languages on
top of the JVM: some of these features, such as the new
\emph{invokedynamic}\footnote{XXX} instruction and the \emph{tail call
  optimization} can probably be exploited by a potential JVM backend to
generate even more efficient code.

>>>>

IronPython and Jython are two popular implementations of Python for,
respectively, the CLI and the JVM, whose approach differs fundamentally from
PyPy.  The source code of PyPy contains a Python interpreter, which the JIT
compiler is automatically generated from: the resulting executable contains
both the interpreter and the compiler, so that it is possible to compile only
the desired parts of the program.  On the other hand, both IronPython and
Jython implements only the compiler: both compile code lazily (when a Python
module is loaded), but since they do not exploit the extra information
potentially available at runtime, it is more a delayed static compilation than
a true JIT one.  As a result, they run Python programs much slower than their
equivalent written in
C\#\footnote{\texttt{http://shootout.alioth.debian.org/gp4/\\benchmark.php?test=all\&lang=iron\&lang2=csharp}}
or
Java\footnote{\texttt{http://blog.dhananjaynene.com/2008/07/performance-\\comparison-c-java-python-ruby-jython-jruby-groovy/}}.

The \emph{Dynamic Language Runtime}\footnote{\texttt{http://www.codeplex.com/dlr}}
(DLR) is a library designed to ease the implementation of dynamic languages
for .NET: IronPython is based on the DLR, so the same remarks apply.

@@

In particular, the \emph{Da Vinci Machine
  Project} \footnote{\texttt{http://openjdk.java.net/projects/mlvm/}} is exploring and
implementing new features to ease the implementation of dynamic languages on
top of the JVM: some of these features, such as the new
\emph{invokedynamic}\footnote{XXX} instruction and the \emph{tail call
  optimization} can probably be exploited by a potential JVM backend to
generate even more efficient code.
